---
title: "clusterGeneration Notes"
author: "Emily Raney"
date: "11/9/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using the clusterGeneration Package

Notes on the documentation for this package can be found in my MA Thesis file on Google Drive. 

### Scenario 1

This scenario is based on a small sample size (mirroring actual fossil data sample size) of thirty observations: 

- three clusters of equal size, with moderate separation;  
- two non-noisy variables (representing some cranial measurements- e.g., cranial capacity and supraorbital torus thickness)- I chose two variables that are less likely to be directly related (rather than something like cranial capacity and cranial length);
- no outliers;
- 3 replicates;
- covMethod is eigen, but I won't set eigenvalues myself;
- all other arguments will be set to default. 


```{r}
library(clusterGeneration)
genRandomClust(3, sepVal = 0.01, numNonNoisy = 2, numNoisy = 0, fileName = "scen1")
```


The output of this function is several files, including a .dat file (space-delimited (?) file containing two columns representing two variables (per the number of non-noisy variables that I specified in the function) and a randomly generated number rows representing observations for both variables). 


The other files are .noisy, .mem, and .log. 

The .log files have details about the data generation including the randomly generated cluster sizes, eigenvalues for each cluster (since I didn't specify them), and information about the covariance matrices. 

The .mem file seems to be a record of which cluster each observation belongs to. 

The .noisy file appears to just be a file with the number of noisy variables in it? Not sure about this one. 

All of the files from this analysis can be found on github. 


#### Plotting Scen 1

The .dat file is delimited with a single space. I pushed the files from the clusterGeneration output up to, then I used the curl package (or did I?) to read the .dat file into R, and then I used the base R plotting function to plot my data. 

This is a plot of Scenario 1 - Replicate 1. 
```{r}
library(curl) #not sure if this is actually necessary
a <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.dat", sep = " ")
scen1_1_plot <- plot(a)
scen1_1_plot
```

I am trying to figure out how to assign a color to each cluster for better visualization, but the problem is that the .mem file has one fewer row than the .dat file, and I can't figure out how to fix this without just editing the files on my local machine. So I can't keep everything on github like I wanted to. I'm still figuring that out, but in the meantime I used the following code: 

```{r}
# scen11_dat <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.dat", sep = " ")
# scen11_mem <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.mem", sep = " ")
# plot_data <- cbind(scen11_dat, scen11_mem)
# plot(plot_data$x1, plot_data$x2, col = plot_data$cluster)
```

Hopefully I can figure out a more elegant solution using ggplot in the future. For now, the plot is on Google Drive. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

Okay now I can't figure out how to 'un-name' the column in the .mem file. I even made a whole new .mem file from scratch to try and fix the problem and all the sudden R is forcing a name on the column anyway so I can't rbind. I'm giving up for now. :-(