---
title: "clusterGeneration Notes"
author: "Emily Raney"
date: "11/9/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using the clusterGeneration Package

Notes on the documentation for this package can be found in my MA Thesis file on Google Drive. 

### Scenario 1


- three clusters of equal size, with moderate separation;  
- two non-noisy variables (representing some cranial measurements- e.g., cranial capacity and supraorbital torus thickness)- I chose two variables that are less likely to be directly related (rather than something like cranial capacity and cranial length);
- no outliers;
- 3 replicates;
- covMethod is eigen, but I won't set eigenvalues myself;
- all other arguments will be set to default.

How to set number of observations?? 


```{r}
library(clusterGeneration)
genRandomClust(3, sepVal = 0.01, numNonNoisy = 2, numNoisy = 0, fileName = "scen1")
```


The output of this function is several files, including a .dat file (space-delimited (?) file containing two columns representing two variables (per the number of non-noisy variables that I specified in the function) and a randomly generated number rows representing observations for both variables). 


The other files are .noisy, .mem, and .log. 

The .log files have details about the data generation including the randomly generated cluster sizes, eigenvalues for each cluster (since I didn't specify them), and information about the covariance matrices. 

The .mem file seems to be a record of which cluster each observation belongs to. 

The .noisy file appears to just be a file with the number of noisy variables in it? Not sure about this one. 

All of the files from this analysis can be found on github. 


#### Plotting Scen 1

The .dat file is delimited with a single space. I pushed the files from the clusterGeneration output up to, then I used the curl package (or did I?) to read the .dat file into R, and then I used the base R plotting function to plot my data. 

This is a plot of Scenario 1 - Replicate 1. 
```{r}
library(curl) #not sure if this is actually necessary
s1_dat <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.dat", sep = " ")
scen1_1_plot <- plot(s1_dat)
scen1_1_plot
```

I am trying to figure out how to assign a color to each cluster for better visualization, but the problem is that the .mem file has one fewer row than the .dat file, and I can't figure out how to fix this without just editing the files on my local machine. So I can't keep everything on github like I wanted to. I'm still figuring that out, but in the meantime I used the following code: 

```{r}
# scen11_dat <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.dat", sep = " ")
# scen11_mem <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.mem", sep = " ")
# plot_data <- cbind(scen11_dat, scen11_mem)
# plot(plot_data$x1, plot_data$x2, col = plot_data$cluster)
```

Hopefully I can figure out a more elegant solution using ggplot in the future. For now, the plot is on Google Drive. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
### Fix for plotting cluster data 

In the read.delim function, the argument header is set to true by default; because of this, R reads the first line of the .mem file as the header and not an observation. I set header to false so that the .mem and .dat files have the same number of lines and can be bound. 

```{r}
scen1_dat_fixed <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.dat", sep = " ") #read in .dat file 
scen1_mem_fixed <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen1_1.mem", sep = " ", header = FALSE, col.names = "cluster") #read in .mem file, set heading to false, add column name 'cluster'

plot1_data <- cbind(scen1_dat_fixed, scen1_mem_fixed) #column binding variable values with the cluster they belong to 
head(plot1_data)

library(ggplot2)
scen1_plot <- ggplot(plot1_data, aes(x = x1, y = x2, color = as.factor(cluster))) +geom_point() +scale_color_manual(values = c("hotpink", "turquoise2", "slateblue1")) + labs(title = "3 clusters, sepVal = 0.01", color = "Cluster") + xlab("Variable 1") + ylab("Variable 2")
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
### Senario 2

One issue I'm having with this package is that I can't figure out how to change the number of observations for each run. I think that will be an important part of the analysis, because I want to see how changing sample sizes affects my output. 

Scenario 2 is identical to Scenario 1, except that Scenario 2 has a sepVal of 0.99 (extremely high separation); additionally, Scenario 2 only has one replicate. 

genRandomClust(3, sepVal = 0.99, numNonNoisy = 2, numNoisy = 0, numReplicate = 1, fileName = "scen2")

scen2_dat <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen2_1.dat", sep = " ", ) #read in .dat file
scen2_mem <- read.delim("https://raw.githubusercontent.com/raneyej/clustergen/master/scen2_1.mem", sep = " ", header = FALSE, col.names = "cluster") #read in .mem file

plot2_data <- cbind(scen2_dat, scen2_mem)
head(plot2_data)

scen2_plot <- ggplot(plot2_data, aes(x = x1, y = x2, color = as.factor(cluster))) +geom_point() +scale_color_manual(values = c("blueviolet", "seagreen2", "orchid1")) + labs(title = "3 clusters, sepVal = 0.99", color = "Cluster") + xlab("Variable 1") + ylab("Variable 2")
scen2_plot